Supplementary Information for Diverse lithic production strategies in southwest China during Late Middle Pleistocene

### 2020-10-06 analysis/paper/paper.Rmd
check SI

---
title: "Supplementary Information for Diverse lithic production strategies in southwest China during Late Middle Pleistocene"
author:
  - Myfirstname Mylastname:
      email: fl@oneplace.edu
      institute: [UofO]
      correspondence: true
  - Yourfirstname Yourlastname:
      email: fl@another.edu
      institute: [UofA]
      correspondence: false
institute:
  - UofO: University of One Place
  - UofA: University of Another Place
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

@@

```{r get-data}
# Note the path that we need to use to access our data files when rendering this document
library(readxl)

@@

@@

# plot
compare_lev_non_lev_mass_plot <- 
ggplot(flakes_L, aes(x = L, 
                     y = mass)) +
  geom_boxplot() +
  geom_quasirandom(alpha = point_alpha) +
  scale_y_log10() + 
  theme_bw() + 
  xlab("") +
  ylab("Mass (g)") +
  ggtitle(paste0("Flake Mass: ", t_test_str_l_mass))
```

@@

# plot
compare_lev_non_lev_maxdim_plot <- 
ggplot(flakes_L, aes(x = L, 
                     y = max_dimension)) +
  geom_boxplot() +
  geom_quasirandom(alpha = point_alpha) +
  scale_y_log10() + 
  theme_bw() + 
  xlab("") +
  ylab("Maximum Dimension (mm)") +
  ggtitle(paste0("Flake Max. Dim.: ", t_test_str_l_maxdim))
```

@@

# plot
compare_lev_non_lev_thick_plot <- 
ggplot(flakes_L, aes(x = L, 
                     y = `Thickness_50%max`)) +
  geom_boxplot() +
  geom_quasirandom(alpha = point_alpha) +
  scale_y_log10() + 
  theme_bw() + 
  xlab("") +
  ylab("Thickness (mm)") +
  ggtitle(paste0("Flake Thickness: ", t_test_str_l_thick))
```

@@

@@

@@

@@

save_plot(here::here("analysis/figures/fig-1-Figures-for-Leva-and-quina.png"),
                     figure_leva_quina,
          base_aspect_ratio = 1,
          base_height = 10, #18,
          base_width =  14) #22)
```

<!-- The following line inserts a page break  -->

# References

<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->

<div id="refs"></div>

>>>>

---
title: "Supplementary Information for Diverse lithic production strategies in southwest China during Late Middle Pleistocene"
---

@@

```{r setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  fig.path = "../figures/",
  dpi = 300
)
```

@@

```{r get-data}
# Note the path that we need to use to access our data files when rendering this document
library(readxl)
library(tidyverse)

@@

tab

@@

# plot
compare_lev_non_lev_mass_plot <- 
ggplot(flakes_L, aes(x = L, 
                     y = mass)) +
  geom_boxplot() +
  geom_quasirandom(alpha = point_alpha) +
  scale_y_log10() + 
  theme_bw() + 
  xlab("") +
  ylab("Mass (g)") +
  ggtitle(paste0("Flake Mass: ", t_test_str_l_mass))

compare_lev_non_lev_mass_plot
```

@@

# plot
compare_lev_non_lev_maxdim_plot <- 
ggplot(flakes_L, aes(x = L, 
                     y = max_dimension)) +
  geom_boxplot() +
  geom_quasirandom(alpha = point_alpha) +
  scale_y_log10() + 
  theme_bw() + 
  xlab("") +
  ylab("Maximum Dimension (mm)") +
  ggtitle(paste0("Flake Max. Dim.: ", t_test_str_l_maxdim))

compare_lev_non_lev_maxdim_plot
```

@@

# plot
compare_lev_non_lev_thick_plot <- 
ggplot(flakes_L, aes(x = L, 
                     y = `Thickness_50%max`)) +
  geom_boxplot() +
  geom_quasirandom(alpha = point_alpha) +
  scale_y_log10() + 
  theme_bw() + 
  xlab("") +
  ylab("Thickness (mm)") +
  ggtitle(paste0("Flake Thickness: ", t_test_str_l_thick))

compare_lev_non_lev_thick_plot
```

@@

compare_qui_non_qui_angle_plot

@@

compare_qui_non_qui_thick_plot

@@

compare_qui_non_qui_giur_plot

@@

save_plot(here::here("analysis/figures/fig-1-Figures-for-Leva-and-quina.png"),
                     figure_leva_quina,
          base_aspect_ratio = 1,
          base_height = 10, #18,
          base_width =  14) #22)

figure_leva_quina
```
